### 2019-03-07 paper/sex_selection_spacing-ver2.tex
Edits of Data section

I exclude visitors to the household, as well as
women who have been married more than once, divorced, or who are 
not living with their husband,
women with inconsistent age at marriage,
and those with missing information on education.
Women interviewed in NFHS-3 or NFHS-4 who were never married or where Gauna 
had not yet been performed were also dropped.
The same goes for women who had at least one multiple births,
reported having a birth before age 12, had a birth before marriage, or
duration between births of less than nine months.
Women who reported less than nine months between marriage and first birth
remain in the sample---unless they are dropped for another reason---because 
8.5\% fall into this category across the four surveys.
Although it is possible that some of these births are premature, the high number of
women who report a birth less than six months after their marriage indicates that for
a majority conception likely occurred before marriage.

@@

Recall error is heavily dependent on how long ago a woman was married 
\citep{Portner2018b}.
I, therefore, drop women married 22 years or more 
for NFHS-1, with the corresponding cut-off points 23 years for NFHS-2, 
and 25 years for NFHS-3 and NFHS-4.
The final sample consists of 
\input{../tables/num_women.tex}
% [number] women, with [number] parity one through four births.

@@

The second group of variables consists of those expected to have an 
approximately proportional effect on the hazard.
These include the length of the first spell 
(for the second and higher-order spells to capture fecundity), 
the age of the mother at the beginning of the spell, 
whether the household owns any land, 
and whether the household belongs to a scheduled tribe or caste.
We cannot observe fecundity directly, but the time from marriage until 
first birth is a suitable proxy because most Indian women do not use 
contraception before the first birth and there is pressure to show that 
a newly married woman can conceive \citep{dyson83,Sethuraman2007,Dommaraju2009}.
The absence of contraception before the first birth is confirmed below by the 
very short spells between marriage and first birth, even among the most educated.
Hence, a long spell between marriage and first birth is likely due to low fecundity.
For both duration from marriage to first birth and the age of the mother at the 
beginning of the spell, I also include their squares.
The remaining variables are dummies for household ownership of land and membership
of a scheduled caste or tribe.

>>>>

I exclude visitors to the household, as well as
women who have been married more than once, divorced, or who are 
not living with their husband,
women with inconsistent age at marriage,
and those with missing information on education.
Women interviewed in NFHS-3 or NFHS-4 who were never married or where Gauna 
had not yet been performed were also dropped.
The same goes for women who had at least one multiple births,
reported having a birth before age 12, had a birth before marriage, or
duration between births of less than nine months.

@@

Recall error is heavily dependent on how long ago a woman was married.%
\footnote{
See the discussion in the online Appendix.
}
I, therefore, drop women married 22 years or more.
The final sample consists of 
\input{../tables/num_women.tex}
% [number] women, with [number] parity one through four births.

@@

The second group of variables consists of those expected to have an 
approximately proportional effect on the hazard.
These include
the age of the mother at the beginning of the spell, 
whether the household owns any land, 
and whether the household belongs to a scheduled tribe or caste.
